---
title: "cointalk"
author: "ed"
date: "4/2/2019"
output: html_document
---


## Coin talk

Here is a analysis of sentiment in Cointalk.

I took all the Cointalk episodes that have transcriptions and ran them through some sentiment analysis. 

Looking at the transcripts, we can see who is more positive , who is more negative, and how that changes over time. 


```{r , include=FALSE,message=FALSE}

library(rvest)
library(here)
library(readr)
library(stringr)
library(tidyverse)
library(tidytext)

first <- function(x){
  z = str_split(x, ":") %>% unlist(.)
  y= unlist(z[[1]])
  return(y[1])}


second <- function(x){
  z = ifelse(str_detect(x,'Jay Kang:'),str_replace(x,'Jay Kang:', ""),x )
  y = ifelse(str_detect(z,'Aaron Lammer:'),str_replace(z,'Aaron Lammer:', ""),z )
  return(y)
}

```


Here is a list of all the cointalk episode webpages that had transcriptions.

```{r, include=FALSE,message=FALSE}


# "https://medium.com/s/cointalk/coin-talk-25-fear-and-loathing-at-a-cryptokitty-auction-33abbcd65b57"


hand_list<- c("https://medium.com/s/cointalk/coin-talk-2-korean-crypto-mania-and-the-kimchi-spread-8ab23de3e1d9",
              "https://medium.com/s/cointalk/coin-talk-3-we-survived-the-crash-w-doug-kim-f3e2c7aebbc2",
              "https://medium.com/s/cointalk/coin-talk-4-do-you-guys-even-believe-in-crypto-own-your-own-casino-5156fa9ff431",
              "https://medium.com/s/cointalk/coin-talk-5-tether-usdt-is-the-new-disneybucks-ef94876ff3b7",
              "https://medium.com/s/cointalk/coin-talk-6-how-low-can-you-go-an-interview-with-jameson-lopp-ab5adf8d3a97",
              "https://medium.com/s/cointalk/7-giancarlo-2020-senate-hearings-on-bitcoin-augurs-first-prediction-marketabout-324e2dd2229c",
              "https://medium.com/s/cointalk/coin-talk-8-interview-with-nocoiner-tech-journalist-adrian-chen-baf00bf05134",
              "https://medium.com/s/cointalk/9-privacy-coins-explained-a-deep-dive-into-monero-xmr-and-zcash-zec-5017b84a7ba3",
              "https://medium.com/s/cointalk/coin-talk-10-telegrams-ton-token-civil-brings-the-blockchain-to-journalism-w-maria-bustillos-913435b278c1",
              "https://medium.com/s/cointalk/coin-talk-12-what-is-an-ico-c94fa9c4226",
              "https://medium.com/s/cointalk/coin-talk-13-did-mt-goxs-japanese-trustee-personally-crash-bitcoin-62f62b65aefb",
              "https://medium.com/s/cointalk/coin-talk-15-whats-so-great-about-the-blockchain-e89c5c5f69b1",
              "https://medium.com/s/cointalk/coin-talk-11-when-dictators-ico-a02bc72da6e1",
              "https://medium.com/s/cointalk/coin-talk-14-whats-so-great-about-the-blockchain-dedc38e9413b",
              "https://medium.com/s/cointalk/coin-talk-16-the-rise-and-fall-of-kang-lammer-americas-worst-crypto-traders-8f32bcb08273",
              "https://medium.com/s/cointalk/coin-talk-18-the-fundamentals-remain-strong-9a8226e2b802",
              "https://medium.com/s/cointalk/coin-talk-19-alt-spring-on-the-campus-quad-1deada76e091",
              "https://medium.com/s/cointalk/coin-talk-20-the-return-of-fomo-kang-w-doug-kim-d3a22a4a3d94",
              "https://medium.com/s/cointalk/coin-talk-21-will-zrx-be-the-next-coin-added-to-coinbase-cedf82567a7c",
              "https://medium.com/s/cointalk/coin-talk-22-%EF%B8%8F-the-bitcoin-ransoming-of-aaronlammer-com-be3072fd2668",
              "https://medium.com/s/cointalk/coin-talk-23-are-ripple-xrp-fans-bots-59c9aa0e192b",
              "https://medium.com/s/cointalk/24-book-club-the-bitcoin-standard-part-1-a0b9ef7981eb",
              "https://medium.com/s/cointalk/coin-talk-26-penguin-jetpacks-w-nathaniel-popper-from-the-new-york-times-44652b88526f",
              "https://medium.com/s/cointalk/coin-talk-27-bitcointopia-where-the-murder-rate-is-100-and-an-interview-with-a-real-xrp-fan-7761ef08d9f5",
              "https://medium.com/s/cointalk/coin-talk-28-book-club-the-bitcoin-standard-part-2-fc0c096583e9",
              "https://medium.com/s/cointalk/episode-29-%EF%B8%8F-r-i-p-sumokoin-eaf69e061178",
              "https://medium.com/s/cointalk/coin-talk-30-interview-with-a-miner-chris-dannen-of-iterative-capital-e36c66b4392b",
              "https://medium.com/s/cointalk/coin-talk-31-kidnapped-by-the-triads-and-other-shitcoin-adventures-abbbd3c53e10",
              "https://medium.com/s/cointalk/coin-talk-32-interview-with-saifedean-ammous-economist-and-author-of-the-bitcoin-standard-39652a6612e5",
              "https://medium.com/s/cointalk/33-how-tezos-went-awry-ed25fb7eab37",
              "https://medium.com/s/cointalk/coin-talk-34-the-real-slim-satoshi-2254252ee6ff",
              "https://medium.com/s/cointalk/coin-talk-35-coinbase-goes-shopping-82d529907499",
              "https://medium.com/s/cointalk/coin-talk-36-how-to-make-dumb-bets-on-augur-w-ledgerstatus-d38d7db33d8f",
              "https://medium.com/s/cointalk/coin-talk-37-decentralized-assassinations-and-pee-tape-markets-c2d062080c2f",
              "https://medium.com/s/cointalk/coin-talk-38-no-market-no-bounce-ft-doug-kim-fc4ce3a86c16",
              "https://medium.com/s/cointalk/coin-talk-39-we-called-a-craigslist-crypto-consultant-58458081de0f",
              "https://medium.com/s/cointalk/coin-talk-40-mailbag-vol-2-4f5cda373118",
              "https://medium.com/s/cointalk/coin-talk-41-where-were-you-when-bcash-forked-c7f6bcd55a89",
              "https://medium.com/s/cointalk/coin-talk-42-excerptoshi-truthers-unite-4eda76b43b0b",
              "https://medium.com/s/cointalk/coin-talk-43-impressions-of-crypto-china-with-chris-dannen-e5e9f87f24e3",
              "https://medium.com/s/cointalk/coin-talk-45-the-psychology-of-mass-movements-with-tony-sheng-7b0376514372",
              "https://medium.com/s/cointalk/46-are-we-ready-to-callabottom-ad9de8faf634",
              "https://medium.com/s/cointalk/coin-talk-47-bitcoin-bugz-weed-stock-mania-1a37507c2313",
              "https://medium.com/s/cointalk/coin-talk-48-senate-hearing-jam-session-pt-1-with-zack-voell-cd1e2e7d62b5",
              "https://medium.com/s/cointalk/coin-talk-49-senate-hearing-jam-session-pt-2-w-brian-patrick-eha-de53e4ebe2b4",
              "https://medium.com/s/cointalk/coin-talk-50-if-vitalik-is-a-9-10-im-a-2-10-an-interview-with-the-new-yorker-s-nick-239364e3ebd5",
              "https://medium.com/s/cointalk/episode-51-but-what-do-you-really-think-about-civil-cvl-2b25c0e1f40e",
              "https://medium.com/s/cointalk/episode-52-hopium-is-a-helluva-drug-w-doug-kim-e0890a77c65b",
              "https://medium.com/s/cointalk/episode-54-are-we-crypto-influencers-4128e2cc7385",
              "https://medium.com/s/cointalk/coin-talk-54-brave-bat-b42293422bbf",
              "https://medium.com/s/cointalk/coin-talk-55-the-bull-case-for-initiative-q-9d7b34c1bda5",
              "https://medium.com/s/cointalk/coin-talk-56-bcash-2-electric-boogaloo-satoshis-vision-bb0389604f7f",
              "https://medium.com/s/cointalk/coin-talk-57-crypto-vs-journalism-cd4242706b33",
              "https://medium.com/s/cointalk/coin-talk-58-super-airdrop-festival-c33752c9c363",
              "https://medium.com/s/cointalk/coin-talk-59-flashbacks-and-fake-beards-a-crypto-2018-year-in-review-77ee1256aeb7",
              "https://medium.com/s/cointalk/coin-talk-60-live-on-the-10th-anniversary-of-the-mining-of-the-genesis-block-a687b7c2959f",
              "https://medium.com/s/cointalk/coin-talk-61-%EF%B8%8Fgrin-the-mimblewimble-protocol-75fe92ed41cf",
              "https://medium.com/s/cointalk/coin-talk-62-fyre-fest-was-the-original-airdrop-f56862e9118d",
              "https://medium.com/s/cointalk/coin-talk-63-ska-selling-out-the-bitcoin-etf-fd7f3a789842",
              "https://medium.com/s/cointalk/cointalk-64-aarons-farm-i-don-t-want-to-mine-in-game-rewards-at-93d47d22b0f9",
              "https://medium.com/s/cointalk/cointalk-65-slanted-and-enchanted-72a36c1d82b",
              "https://medium.com/s/cointalk/cointalk-%EF%B8%8F-66-hxro-is-a-crypto-game-that-is-definitely-not-gambling-47595a6c84d5",
              "https://medium.com/s/cointalk/episode-67-would-oprah-move-the-needle-5b20d9a7910d",
              "https://medium.com/s/cointalk/cointalk-%EF%B8%8F-68-%EF%B8%8F-hacking-team-wants-to-connect-on-linked-in-90220f283a57"
              )

```


```{r,include=FALSE,message=FALSE}

# reading in the first webpage

testtesttest <- read_html(hand_list[[1]])

# pulling only the parts that are attributed to Jay or Aaron

testtibble<- testtesttest %>% 
  html_nodes('p') %>% 
  html_text() %>% 
  as_tibble() %>% 
  filter(str_detect(value,"Jay Kang:")==TRUE |str_detect(value,"Aaron Lammer:")==TRUE) 

# getting the episode number from the webpage

episode <- testtesttest %>% html_nodes('h1') %>% html_text()

# pulling all of the text attributed to Jay and Aaron

text <- testtibble$value
new_text <- unlist(text)

# Each block of text starts with the name of the speaker and then ":" and then what they said.
# The next block splits the text into two lists, one is the name of the speaker and the other is what he said.


test1<- map(new_text,first)
test2<- map(new_text,second)


# this takes the two lists and makes them into a dataframe
conversation_df <- tibble(name = unlist(test1),text = test2)

#adding the row number and the episode number to each row
conversation_df <-  conversation_df %>% mutate(linenumber=row_number(),episode=episode)

# now createing a tibble containing one row for each word.

tidy_conversation <- conversation_df %>% 
  unnest_tokens(word, text) 


# removing stop words

tidy_conversation <- tidy_conversation %>% 
  anti_join(stop_words)

# renaming the tibble 'tidy_conversation_main' which will be where all the tibbles are appended to 

tidy_conversation_main <- tidy_conversation

```


```{r, include=FALSE,message=FALSE}

# creating a number list for each link in the list of podcast links.

hand_listnum <- c(2:length(hand_list))

# episode 24 transcript is not formated correctly so I took it out. 


# a for loop that goes through each link, pulls the html, and does the same parsing and wrangling that was done to the first webpage.

for(number in hand_listnum){
  print(number)
  
  testtesttest <- read_html(hand_list[[number]])
  
  testtibble<- testtesttest %>% 
    html_nodes('p') %>% 
    html_text() %>% 
    as_tibble() %>% 
    filter(str_detect(value,"Jay Kang:")==TRUE | str_detect(value,"Aaron Lammer:")==TRUE 
           |str_detect(value,"Jay:")==TRUE |str_detect(value,"Aaron:")==TRUE) 
  
  episode <- testtesttest %>% html_nodes('h1') %>% html_text()
  print(episode)
  
  text <- testtibble$value
  
  new_text <- unlist(text)
  
  test1<- map(new_text,first)
  test2<- map(new_text,second)
  
  conversation_df <- tibble(name = unlist(test1),text = test2)
  
  conversation_df <-  conversation_df %>% mutate(linenumber=row_number(),episode=episode)
  
  tidy_conversation <- conversation_df %>% 
    unnest_tokens(word, text) 
  
  tidy_conversation <- tidy_conversation %>% 
    anti_join(stop_words)
  
  tidy_conversation_main <- rbind(tidy_conversation_main,tidy_conversation)
  
}

```

Now we have a table with  "name","linenumber","episode","word".  

```{r,include=FALSE}
head(tidy_conversation_main)

```

I join three sentiment tables to that table, one from Bing, one from Afinn, and one from NRC.  


```{r,include=FALSE,message=FALSE}

# bringing in all of the bing sentiment words
bing  <- get_sentiments('bing')
afinn <- get_sentiments('afinn')
nrc   <- get_sentiments('nrc')

# joining the sentiment word table to the coin talk table


# taking out the word 'grin' since it referes to a coin and not the actually grining, which is positive

tidy_conversation_main <- tidy_conversation_main %>% filter(word != 'grin')




convo_w_bing <- tidy_conversation_main %>%
  # With inner join, implement sentiment analysis using `bing`
  inner_join(bing)

convo_w_bing <- convo_w_bing  %>%
  # With inner join, implement sentiment analysis using `bing`
  inner_join(afinn)


convo_w_bing <- convo_w_bing  %>%
  # With inner join, implement sentiment analysis using `bing`
  inner_join(afinn)





colnames(nrc)[2] <- 'nrc_sentiment'

convo_w_bing <- convo_w_bing  %>%
  # With inner join, implement sentiment analysis using `bing`
  inner_join(nrc)

# coding negative as a zero and positive sentiment as a one.

convo_w_bing <- convo_w_bing %>% mutate(bing_score = ifelse(sentiment == 'negative',0,1))


# a couple of the episodes either just said the speakers first name instead of their full name. 

convo_w_bing <- convo_w_bing %>% mutate(name = ifelse(name=="Aaron Lammer","Aaron",
                                      ifelse(name== "Jay Kang","Jay",name)))

# here, I am extracting the episode

convo_w_bing <- convo_w_bing %>%
mutate(episode_number = ifelse(is.na(str_extract(episode,'[:digit:]{2}')),str_extract(episode,'[:digit:]'),str_extract(episode,'[:digit:]{2}'))%>% as.numeric())

                        
summary_of_episode <- left_join(convo_w_bing %>%  group_by(name,episode) %>%
                                  summarize(bing_total=sum(bing_score),afinn_total = sum(score)),convo_w_bing %>%
                                  group_by(name,episode) %>% 
                                  tally()) %>%
                                  mutate(bing_sentiment_score = bing_total/n, 
                                         afinn_sentiment_score = afinn_total/n)


summary_of_episode <- summary_of_episode %>% 
                      mutate(episode_number = ifelse(is.na(str_extract(episode,'[:digit:]{2}')),str_extract(episode,'[:digit:]'),str_extract(episode,'[:digit:]{2}')))


summary_of_episode$episode_number <- as.numeric(summary_of_episode$episode_number)



```


The first graph shows the over Bing sentiment score showing the percentage positive words as a total of non-stop words over time.


Please note that I had to take the word 'grin' out of the analysis, since it is refering to a (maybe shit?) coin, and not to them grinning all the time. 

```{r, echo=FALSE,message=FALSE}

ggplot(summary_of_episode,aes(episode_number,bing_sentiment_score,color=name)) +
  geom_point() +
  geom_smooth(method='lm')

```

It looks like Aaron starts out more positive than Jay, but over time the two seem to start to converage. 



afinn_sentiment_score 

Using the Afinn table, the look like they start out even more far apart, but show the same general trend of move towards the same amount of negativity on crypto currency.  

```{r, echo=FALSE,message=FALSE}

ggplot(summary_of_episode,aes(episode_number,afinn_sentiment_score,color=name)) +
  geom_point() +
  geom_smooth(method='lm')

```




Fear  

There's a lot to be afraid of in the crypto world. This graph uses the NRC sentiment table to show the percentage of fear words over time. 


```{r, echo=FALSE,message=FALSE}

 fear_graph_df <- convo_w_bing %>% filter(nrc_sentiment=='fear') %>% group_by(name,episode_number,nrc_sentiment) %>% tally()

ggplot(fear_graph_df,aes(episode_number,n,color=name)) +
  geom_point()+
  geom_smooth(method='lm')

```


Looks like Aaron has caught up to Jay.  


Joy  



```{r, echo=FALSE,message=FALSE}

joy_graph_df <- convo_w_bing %>% 
  filter(nrc_sentiment=='joy') %>% 
  group_by(name,episode_number,nrc_sentiment) %>% 
  tally()

ggplot(joy_graph_df,aes(episode_number,n,color=name)) +
  geom_point()+
  geom_smooth(method='lm')

```

Although there are more words about fear, there are also more words about joy from Aaron.


 unique(convo_w_bing$nrc_sentiment)
 [1] "anger"        "disgust"      "fear"         "negative"     "sadness"     
 [6] "anticipation" "joy"          "positive"     "trust"        "surprise" 
 
 
 Anger  
 
```{r, echo=FALSE,message=FALSE}

anger_graph_df <- convo_w_bing %>% filter(nrc_sentiment=='anger') %>% group_by(name,episode_number,nrc_sentiment) %>% tally()

ggplot(anger_graph_df,aes(episode_number,n,color=name)) +
  geom_point()+
  geom_smooth(method='lm')

```


Looks like Aaron was less angry than Jay at the start of the podcast, but now has passed him, maybe those are the bags talking.

